---
title: "Advanced Visualization in R Term Project"
output:
  html_document:
    toc: true
    toc_float: true
---
414333 - Özgür Polat \
417121 - Hüseyin Can Minareci

## Introduction
With more and more consumers abandoning their credit card programs, a manager at the bank is concerned. They would really appreciate if one could foresee who would be churned for them so that they can proactively go to the consumer and offer better value to them and turn the decisions of customers in the opposite direction. Thus, they aggregated this dataset and the source we acquired it received it from https://leaps.analyttica.com/ 

Here in this project we will try to enlight the big picture a bit more with the capabilities we gained thanks to the Advanced Visualization in R course in Faculty of Economical Sciences at the University of Warsaw.

## Data Definition
It is the best to start with understanding the variables we have and their definitions.

* **CLIENTNUM**: Client number. Unique identifier for the customer holding the account
* **Attrition_Flag**: Internal event (customer activity) variable - if the account is closed then 1 else 0
* **Customer_Age**: Demographic variable - Customer's Age in Years
* **Gender**: Demographic variable - M=Male, F=Female
* **Dependent_count**: Demographic variable - Number of dependents
* **Education_Level**: Demographic variable - Educational Qualification of the account holder (example: high school, college graduate, etc.)
* **Marital_Status**: Demographic variable - Married, Single, Divorced, Unknown
* **Income_Category**: Demographic variable - Annual Income Category of the account holder (< $40K, $40K - 60K, $60K - $80K, $80K-$120K, > $120K, Unknown)
* **Card_Category**: Product Variable - Type of Card (Blue, Silver, Gold, Platinum)
* **Months_on_book**: Period of relationship with bank
* **Total_Relationship_Count**:Total no. of products held by the customer
* **Months_Inactive_12_mon**: No. of months inactive in the last 12 months
* **Contacts_Count_12_mon**: No. of Contacts in the last 12 months
* **Credit_Limit**: Credit Limit on the Credit Card
* **Total_Revolving_Bal**:Total Revolving Balance on the Credit Card
* **Avg_Open_To_Buy**: Open to Buy Credit Line (Average of last 12 months)
* **Total_Amt_Chng_Q4_Q1**: Change in Transaction Amount (Q4 over Q1)
* **Total_Trans_Amt**: Total Transaction Amount (Last 12 months)
* **Total_Trans_Ct**: Total Transaction Count (Last 12 months)
* **Total_Ct_Chng_Q4_Q1**: Change in Transaction Count (Q4 over Q1)
* **Avg_Utilization_Ratio**: Average Card Utilization Ratio
* **Naive_Bayes_Classifier_Attrition_Flag_Card_Category_Contacts_Count_12_mon_Dependent_count_Education_Level_Months_Inactive_12_mon_1**: Naive Bayes
* **Naive_Bayes_Classifier_Attrition_Flag_Card_Category_Contacts_Count_12_mon_Dependent_count_Education_Level_Months_Inactive_12_mon_2**: Naive Bayes


## Library Imports
```{r,, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gridExtra)
library(cowplot)
library(ggforce)
library(GGally)
library(ggpubr)
```

## Data Import
```{r}
churn <- read.csv("Data/churn.csv", sep = ',', stringsAsFactors = TRUE)

churnN <- read.csv("Data/churn.csv", sep = ',', na.strings = c("NA", "N/A", "Unknown"), stringsAsFactors = TRUE)
```

## Data Preparation

```{r}
colSums(churn[,c(6,7,8)]=="Unknown")
## I think we should remove those Unknowns

churnNN <- drop_na(churnN)

## Drop ClientNum column here
## Make Attrition Flag 1-0
```

```{r}
prop.table(table(churn$Attrition_Flag))
```
```{r}
prop.table(table(churnNN$Attrition_Flag))
```
After dropping Unknowns we are having very similar distribution and I would say lets drop it in order to have better EDA 
```{r}

summary(churn)

```

```{r}
### I don't remember why we did Attrition_Flag 0-1??? Doesn't make sense now so I comment it out if you will need uncomment line 91 and tell me for what we are gonna use it.
# If customer left the bank 1 if stayed 0

# churnNN$Attrition_Flag <- ifelse(churnNN$Attrition_Flag=="Attrited Customer", 1, 0)

# dropping the columns which is not useful for our analysis
churnNN$CLIENTNUM <- NULL
churnNN$Naive_Bayes_Classifier_Attrition_Flag_Card_Category_Contacts_Count_12_mon_Dependent_count_Education_Level_Months_Inactive_12_mon_1 <- NULL
churnNN$Naive_Bayes_Classifier_Attrition_Flag_Card_Category_Contacts_Count_12_mon_Dependent_count_Education_Level_Months_Inactive_12_mon_2 <- NULL

```


```{r}

summary(churnNN)

```


```{r}
# Ordering factor from smaller to bigger in order to have it in correct order in plots

churnNN$Income_Category <- ordered(churnNN$Income_Category, levels = c("Less than $40K", "$40K - $60K", "$60K - $80K", "$80K - $120K", "$120K +"))
churnNN$Education_Level <- ordered(churnNN$Education_Level, levels = c("Uneducated", "High School", "College", "Graduate","Post-Graduate",  "Doctorate"))


```

## Exploratory Data Analysis


### Plot 1



```{r}

ggplot(churnNN, aes(x = Credit_Limit, fill = Income_Category)) + 
  geom_histogram(data = churnNN[,-8], fill = "grey", alpha = .5) + 
  geom_histogram(colour = "black") +
  facet_wrap(~ Income_Category) + 
  guides(fill = FALSE)
  

```
```{r}

ggplot(churnNN, aes(x = Total_Revolving_Bal, fill = Attrition_Flag)) + 
  geom_histogram(data = churnNN[,-1], fill = "grey", alpha = .5) + 
  geom_histogram(colour = "black") +
  facet_wrap(~ Attrition_Flag) + 
  guides(fill = FALSE)
  

```



### Plot 2

Explanation of this plot will be added...

```{r}
my_comp <- list( c("Uneducated", "High School"), c("High School", "College"), c("College", "Graduate"), c("Graduate", "Post-Graduate"), c("Post-Graduate", "Doctorate") )

ggviolin(churnNN, x = "Education_Level", y = "Total_Revolving_Bal",
          fill = "Education_Level", palette = "jco",
          add = "boxplot", add.params = list(fill = "white"))  + 
  stat_compare_means(method = 'anova') +
  stat_compare_means(comparisons = my_comp)
```

### Plot 3
#### Correlation plot
```{r, message=FALSE}
library(heatmaply)
library(plotly)
library(ggcorrplot)
churn_numeric <- select_if(churnNN, is.numeric)

churn_ready_for_corr <- churn_numeric %>% 
  select(1:14)


# Compute correlation coefficients
corr <- churn_ready_for_corr %>% 
  cor()


# Compute correlation p-values
cor.test.p <- function(x){
    FUN <- function(x, y) cor.test(x, y)[["p.value"]]
    z <- outer(
      colnames(x), 
      colnames(x), 
      Vectorize(function(i,j) FUN(x[,i], x[,j]))
    )
    dimnames(z) <- list(colnames(x), colnames(x))
    z
}
p <- cor.test.p(churn_ready_for_corr)

# Create the heatmap
heatmaply_cor(
  corr,
  node_type = "scatter",
  point_size_mat = -log10(p), 
  point_size_name = "-log10(p-value)",
  label_names = c("x", "y", "Correlation")
)

```





### PLot 4

#### Cluster Analysis

Placeholder

```{r}
# Clustering Variables

clusterData <- churnNN[, c("Credit_Limit", "Total_Revolving_Bal")]

clusters2 <- kmeans(clusterData, 3)


palette(c("#E41A1C", "#377EB8", "#4DAF4A",
          "#984EA3", "#FF7F00", "#FFFF33",
          "#A65628", "#F781BF", "#999999"))

par(mar = c(5.1, 4.1, 0, 1))
plot(clusterData,
     col = clusters2$cluster,
     pch = 20, cex = 3)
points(clusters2$centers, pch = 3, cex = 3, lwd = 3)


```



## Conclusion















































