---
title: "Advanced Visualization in R Term Project"
output: 
  flexdashboard::flex_dashboard:
    theme: cerulean
    orientation: rows
    vertical_layout: fill
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("Vis_Project.R")
```

Introduction
================================

## Data Definition

### It is the best to start with understanding the variables we have and their definitions.

- **CLIENTNUM**: Client number. Unique identifier for the customer holding the account
- **Attrition_Flag**: Internal event (customer activity) variable - if the account is closed then 1 else 0
- **Customer_Age**: Demographic variable - Customer's Age in Years
- **Gender**: Demographic variable - M=Male, F=Female
- **Dependent_count**: Demographic variable - Number of dependents
- **Education_Level**: Demographic variable - Educational Qualification of the account holder (example: high school, college graduate, etc.)
- **Marital_Status**: Demographic variable - Married, Single, Divorced, Unknown
- **Income_Category**: Demographic variable - Annual Income Category of the account holder (< $40K, $40K - 60K, $60K - $80K, $80K-$120K, > $120K, Unknown)
- **Card_Category**: Product Variable - Type of Card (Blue, Silver, Gold, Platinum)
- **Months_on_book**: Period of relationship with bank
- **Total_Relationship_Count**:Total no. of products held by the customer
- **Months_Inactive_12_mon**: No. of months inactive in the last 12 months
- **Contacts_Count_12_mon**: No. of Contacts in the last 12 months
- **Credit_Limit**: Credit Limit on the Credit Card
- **Total_Revolving_Bal**:Total Revolving Balance on the Credit Card
- **Avg_Open_To_Buy**: Open to Buy Credit Line (Average of last 12 months)
- **Total_Amt_Chng_Q4_Q1**: Change in Transaction Amount (Q4 over Q1)
- **Total_Trans_Amt**: Total Transaction Amount (Last 12 months)
- **Total_Trans_Ct**: Total Transaction Count (Last 12 months)
- **Total_Ct_Chng_Q4_Q1**: Change in Transaction Count (Q4 over Q1)
- **Avg_Utilization_Ratio**: Average Card Utilization Ratio
- **Naive_Bayes_Classifier_Attrition_Flag_Card_Category_Contacts_Count_12_mon_Dependent_count_Education_Level_Months_Inactive_12_mon_1**: Naive Bayes
- **Naive_Bayes_Classifier_Attrition_Flag_Card_Category_Contacts_Count_12_mon_Dependent_count_Education_Level_Months_Inactive_12_mon_2**: Naive Bayes


Overview
================================

```{r}
library(shinydashboard)
avgtrans <- round(mean(churnNN$Total_Trans_Amt),2)
avg_lim <- mean(churnNN$Credit_Limit)
avg_age <- trunc(mean(churnNN$Customer_Age))
totaltrans <- sum(churnNN$Total_Trans_Amt)
avg_rel <- round(mean(churnNN$Months_on_book),2)
no_customer <- nrow(churnNN)


ui <- dashboardPage(skin = "black",
                    dashboardHeader(disable = TRUE),
                    dashboardSidebar(disable = TRUE),
                    dashboardBody(
    tags$head(
      tags$style(HTML("body {overflow-y: hidden;}"))

  ),
                        fluidRow(
                            valueBoxOutput("customer", width = 4),
                            valueBoxOutput("avgage", width = 4),
                            valueBoxOutput("avg_rel", width = 4),                            
                            valueBoxOutput("test_box", width = 4),
                            valueBoxOutput("avglim", width = 4),
                            valueBoxOutput("totaltrans", width = 4)
                        )
                    )
)
# Server response
server <- function(input, output) {
        output$customer <- renderValueBox({
          no_customer %>%
            formatC(1:10 * 100000, format="d", big.mark=",") %>%
            shinydashboard::valueBox("Number of Customer",
                     icon = icon("signal"),
                     color = "navy"
        )
    }) 
        output$avgage <- renderValueBox({
            shinydashboard::valueBox(value = avg_age, "Average Customer Age",
                                     icon = icon("thumbs-up", lib = "glyphicon"),
                                     color = "green"
        )
    })
        output$avg_rel <- renderValueBox({
            shinydashboard::valueBox(value= avg_rel, "Average Period of Relationship",
                     icon = icon("flag"),
                     color = "orange"
        )
    })
        output$test_box <- renderValueBox({
          avgtrans %>%
            formatC(1:10 * 100000, format="d", big.mark=",") %>%
            shinydashboard::valueBox("Average Transaction",
                     icon = icon("chart-area"),
                     color = "blue"
        )
    })
    output$avglim <- renderValueBox({
      avg_lim %>%
            formatC(1:10 * 100000, format="d", big.mark=",") %>%
            shinydashboard::valueBox("Average Credit Limit",
                     icon = icon("balance-scale-right"),
                     color = "purple"
        )
    })
         output$totaltrans <- renderValueBox({
           totaltrans %>%
            formatC(1:10 * 100000, format="d", big.mark=",") %>%
            shinydashboard::valueBox("Total Transaction",
                                     icon = icon("chart-pie"),
                                      color = "red"
        )
    })
}

shinyApp(ui, server)
```

Row 
-----------------------------------------------------------------------

### Attrition Flag
 
```{r}
library(plotly)
fig <- churnNN %>% count(Attrition_Flag)
fig %>% plot_ly(labels = ~Attrition_Flag, values = ~n)  %>% add_pie(hole = 0.60)
```


### Gender

```{r}
fig1 <- churnNN %>% count(Gender)
fig1 %>% plot_ly(labels = ~Gender, values = ~n)  %>% add_pie(hole = 0.60)
```

### Marital Status

```{r}
library(plotly)
fig2 <- churnNN %>% count(Marital_Status)
fig2 %>% plot_ly(labels = ~Marital_Status, values = ~n)  %>% add_pie(hole = 0.60)
```


Analysis
================================

Row 
-----------------------------------------------------------------------

### Income Category

```{r Income_Category}
p1<- ggplot(churnNN, aes(x = Income_Category)) +
  geom_bar(aes(fill = Attrition_Flag)) +
  geom_text(aes(y = ..count.. -200, label = paste0(round(prop.table(..count..),4) * 100, '%')), 
            stat = 'count', position = position_dodge(.1), size = 3) + 
  scale_fill_manual(values=c("#ff7f0e","#1f77b4")) + 
  theme_gdocs()+ theme(axis.title = element_text(face = "bold", color = "#ff7f0e")) +
  labs(y="Count", x = "Income Category", fill = "Attrition Flag")

ggplotly(p1)
```

### Card Category

```{r Card_Category}
p2<-ggplot(churnNN, aes(x = Card_Category)) +
  geom_bar(aes(fill = Attrition_Flag)) +
  geom_text(aes(y = ..count.. -200, label = paste0(round(prop.table(..count..),4) * 100, '%')), 
            stat = 'count', position = position_dodge(.1), size = 3) + 
  scale_fill_manual(values=c("#ff7f0e","#1f77b4")) + 
  theme_gdocs()+ theme(axis.title = element_text(face = "bold", color = "#ff7f0e")) +
  labs(y="Count", x = "Card Category", fill = "Attrition Flag")

ggplotly(p2)

```

Row 
-----------------------------------------------------------------------

### Education Level

```{r Education_Level}
p3<- ggplot(churnNN, aes(x = Education_Level)) +
  geom_bar(aes(fill = Attrition_Flag)) +
  geom_text(aes(y = ..count.. -200, label = paste0(round(prop.table(..count..),4) * 100, '%')), 
            stat = 'count', position = position_dodge(.1), 
            size = 3) + scale_fill_manual(values=c("#ff7f0e","#1f77b4")) + 
  theme_gdocs() + theme(axis.title = element_text(face = "bold", color = "#ff7f0e")) + 
  labs(y="Count", x = "Education Level", fill = "Attrition Flag")

ggplotly(p3)

```

### Marital Status

```{r Marital_Status}
p4<-ggplot(churnNN, aes(x = Marital_Status)) +
  geom_bar(aes(fill = Attrition_Flag)) +
  geom_text(aes(y = ..count.. -200, label = paste0(round(prop.table(..count..),4) * 100, '%')), 
            stat = 'count', position = position_dodge(.1), 
            size = 3) + scale_fill_manual(values=c("#ff7f0e","#1f77b4")) + 
  theme_gdocs() + theme(axis.title = element_text(face = "bold", color = "#ff7f0e")) + 
  labs(y="Count", x = "Marital Status", fill = "Attrition Flag")

ggplotly(p4)
```


Analysis Part 2
================================
Row 
-----------------------------------------------------------------------

### Existing Customer
```{r Existing}
ex <- ggplot(data =subset(churnNN, Attrition_Flag=="Existing Customer"), aes(x=Customer_Age,fill=Gender)) +
  geom_bar() + theme_gdocs() + ggtitle("Distrubiton of Age among Existing Customers") + 
  theme(plot.title = element_text(color = "#1f77b4", size = 15),axis.title = element_text(face = "bold", color = "#ff7f0e")) + labs(y="Count", x = "Customer Age") +
  scale_fill_manual(values=c("#ff7f0e","#1f77b4"))

ggplotly(ex)

```

### Attrited Customer

```{r Attrited}
at <- ggplot(data =subset(churnNN, Attrition_Flag=="Attrited Customer"), aes(x=Customer_Age,fill=Gender)) +
  geom_bar() + theme_gdocs() + ggtitle("Distrubiton of Age among Attrited Customers") + 
  theme(plot.title = element_text(color = "#1f77b4", size = 15),axis.title = element_text(face = "bold", color = "#ff7f0e")) + labs(y="Count", x = "Customer Age") +
  scale_fill_manual(values=c("#ff7f0e","#1f77b4"))

ggplotly(at)
```

Row 
-----------------------------------------------------------------------

### Existing Customer by Categorical Variables

```{r}
library(gridExtra)
library(grid)

churn_ex <- subset(churnNN, Attrition_Flag=="Existing Customer")
colors <- c("#1f77b4","#ff7f0e" ,"#2ca02c", "#d62728", "#9467bd")
fig <- plot_ly()
fig <- fig %>% add_pie(data = count(churn_ex, Income_Category), labels = ~Income_Category, values = ~n,
                       textposition = 'inside', name = "Income Category", domain = list(row = 0, column = 0))

fig <- fig %>% add_pie(data = count(churn_ex, Marital_Status), labels = ~Marital_Status, values = ~n,
                       textposition = 'inside', name = "Marital Status", domain = list(row = 1, column = 1),
                       marker = list(colors = colors, line = list(color = '#FFFFFF', width = 1)))
fig <- fig %>% add_pie(data = count(churn_ex, Card_Category), labels = ~Card_Category, values = ~n, 
                       textposition = 'inside', name = "Card Category", domain = list(row = 0, column = 1),
                       marker = list(colors = colors, line = list(color = '#FFFFFF', width = 1)))
fig <- fig %>% add_pie(data = count(churn_ex, Education_Level), labels = ~Education_Level, values = ~n,
                       textposition = 'inside', name = "Education Level", domain = list(row = 1, column = 0),
                       marker = list(colors = colors, line = list(color = '#FFFFFF', width = 1)))

fig <- fig %>% layout(title = "Pie Charts with Subplots", showlegend = F,
                      grid=list(rows=2, columns=2),
                      xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                      yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig

```

### Attried Customer by Categorical Variables

```{r}

churn_at <- subset(churnNN, Attrition_Flag=="Attrited Customer")
colors <- c("#1f77b4","#ff7f0e" ,"#2ca02c", "#d62728", "#9467bd")
fig1 <- plot_ly()
fig1 <- fig1 %>% add_pie(data = count(churn_at, Income_Category), labels = ~Income_Category, values = ~n,
                         textposition = 'inside', name = "Income Category", domain = list(row = 0, column = 0))
fig1 <- fig1 %>% add_pie(data = count(churn_at, Card_Category), labels = ~Card_Category, values = ~n,
                         textposition = 'inside', name = "Card Category", domain = list(row = 0, column = 1),
                         marker = list(colors = colors,line = list(color = '#FFFFFF', width = 0.5)))
fig1 <- fig1 %>% add_pie(data = count(churn_at, Education_Level), labels = ~Education_Level, values = ~n,
                         textposition = 'inside', name = "Education Level", domain = list(row = 1, column = 0),
                         marker = list(colors = colors,line = list(color = '#FFFFFF', width = 1)))
fig1 <- fig1 %>% add_pie(data = count(churn_at, Marital_Status), labels = ~Marital_Status, values = ~n,
                         textposition = 'inside', name = "Marital Status", domain = list(row = 1, column = 1),
                         marker = list(colors = colors, line = list(color = '#FFFFFF', width = 1)))
fig1 <- fig1 %>% layout(title = "Pie Charts with Subplots", showlegend = F,
                       grid=list(rows=2, columns=2),
                       xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                       yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))

fig1

```

Analysis Part 3
================================

Row 
-----------------------------------------------------------------------

### Total Revolving Balance by Education Level
```{r}
my_comp <- list( c("Uneducated", "High School"), c("High School", "College"), c("College", "Graduate"), c("Graduate", "Post-Graduate"), c("Post-Graduate", "Doctorate") )

ggviolin(churnNN, x = "Education_Level", y = "Total_Revolving_Bal",
         fill = "Education_Level", palette = "jco",
         add = "boxplot", add.params = list(fill = "white"))  + 
  stat_compare_means(method = 'anova') +
  stat_compare_means(comparisons = my_comp)
```

### Total Revolving Balance on the Credit Card
```{r}
ggplot(churnNN, aes(x = Total_Revolving_Bal, fill = Attrition_Flag)) + 
  geom_histogram(data = churnNN[,-1], fill = "grey", alpha = .5) + 
  geom_histogram(colour = "black") +
  facet_wrap(~ Attrition_Flag) + 
  guides(fill = FALSE) +
  xlab("Total Revolving Balance on the Credit Card")+
  ylab("Number of Customers")
```

Row 
-----------------------------------------------------------------------

### Credit Limit on the Credit Card
```{r}
ggplot(churnNN, aes(x = Credit_Limit, fill = Income_Category)) + 
  geom_histogram(data = churnNN[,-7], fill = "grey", alpha = .5) + 
  geom_histogram(colour = "black") +
  facet_wrap(~ Income_Category) + 
  guides(fill = FALSE) +
  xlab("Credit Limit on the Credit Card")
```

### Trend
```{r}
sct <- ggplot(churnNN,aes(Customer_Age,Credit_Limit))+ geom_point() +geom_smooth()
sct+theme_gdocs()
```


Analysis Part 4
================================

### Correlation 

```{r}
churncor <- churnNN[sapply(churnNN, is.numeric)]
x <- cor(churncor)

corplot <- hchart(x) %>% 
  hc_legend(layout = "vertical",
            align = "right",
            verticalAlign = "bottom") %>% 
  hc_plotOptions(
    series = list(
      dataLabels = list(
        enabled = TRUE,
        formatter = JS("function(){
                                   return Highcharts.numberFormat(this.point.value, 2);
                                   }"))))
corplot

```
### Regression 

```{r}

```

Can'in Yeri
================================

```{r}

ui <- dashboardPage(skin = "black",
                    dashboardHeader(disable = TRUE),
                    dashboardSidebar(disable = TRUE),
                    dashboardBody(
    tags$head(
      tags$style(HTML("body {overflow-y: hidden;}"))

  ),
                        fluidRow(
                            tags$b("Average Credit Limit"),
                        awesomeRadio(inputId = "grp",
                                                "Select Group:",
                                                c("Attrition_Flag", "Gender","Education_Level", "Marital_Status", "Income_Category", "Card_Category"),
                                                selected = c("Attrition_Flag"),
                                                inline = TRUE,
                                                status = "danger"
                 ),highchartOutput("heatmap")
                        )
                    )
)
# Server response
server <- function(input, output) {
heat_attrition <-reactive({churnNN %>% group_by(.dots = input$grp) %>% summarise(Average_credit = round(mean(Credit_Limit)))%>% arrange(desc(Average_credit))})
    
htc <- reactive({
      if(input$grp=="Attrition_Flag"){
        htc <- heat_attrition() %>% hchart(type = "treemap", hcaes(x = Attrition_Flag, value = Average_credit, color = Average_credit))
      } else if(input$grp=="Gender"){
        htc <- heat_attrition() %>% hchart(type = "treemap", hcaes(x = Gender, value = Average_credit, color = Average_credit))
      } else if(input$grp=="Education_Level"){
        htc <- heat_attrition() %>% hchart(type = "treemap", hcaes(x = Education_Level, value = Average_credit, color = Average_credit))
      } else if(input$grp=="Marital_Status"){
        htc <- heat_attrition() %>% hchart(type = "treemap", hcaes(x = Marital_Status, value = Average_credit, color = Average_credit))
      } else if(input$grp=="Income_Category"){
        htc <- heat_attrition() %>% hchart(type = "treemap", hcaes(x = Income_Category, value = Average_credit, color = Average_credit))
      } else if(input$grp=="Card_Category"){
        htc <- heat_attrition() %>% hchart(type = "treemap", hcaes(x = Card_Category, value = Average_credit, color = Average_credit))
      } 
      htc  %>% hc_title(text = paste("Average Credit Limit based on",input$grp)) %>%   hc_add_theme(hc_theme_google()) %>% hc_credits(enabled = TRUE, text = "", style = list(fontSize = "10px")) %>%
        hc_colorAxis(minColor = "#32CD32", maxColor = "#00008B")}) 

  

    output$heatmap<- renderHighchart({
      htc()
    }
    )
}

shinyApp(ui, server)
```

